### 2015-06-05 adp.tex
address some comments

%!TEX root =  autocontgrlp.tex
\section{Approximate Dynamic Programming}
\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables. \todoc{This itself won't be a curse, would it be? The problem is that the computation cost also grows exponentially. Note that we never defined what we mean by state variables.}
Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.

\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.

\subsection{Linear Function Approximation}
The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Approximate Dynamic Programming}
\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states and computational costs grow exponentially in the dimensions of the state space. \todoc{This itself won't be a curse, would it be? The problem is that the computation cost also grows exponentially. Note that we never defined what we mean by state variables.}
Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parametrizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.

\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parametrized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parametrized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.

\subsection{Linear Function Approximation}
The most widely used parametrized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.

### 2015-06-05 alubp.tex
address some comments

(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb i=1,\ldots,n,

@@

r_c\stackrel{\Delta}{=} & \argmin_{r\in \chi} c^\top \Phi r,\nn\\

@@

The proof follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$.
Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. 

@@

@@

||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\
&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
&=\frac{\epsilon+\beta}{1-\alpha}.

>>>>

(\hg J)(i)\stackrel{\Delta}{=}(\Phi r_{e_i,J})(i), \mb i=1,\ldots,n,

@@

r_{c,J}\stackrel{\Delta}{=} & \underset{r\in \N}{\argmin}\mb c^\top \Phi r,\nn\\

@@

The proof follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$.\par
We need to show $V_1\le V_0 \le \hj$ and then the desired result follows from Lemma~\ref{tgmonotone}. Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. Now, for showing that $V_1 \le V_0$ holds, fix any $i$. We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r_{e_i,V_0})(i) \leq V_0(i)$. By the definition of $r_{e_i,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$. Thus, it suffices to show that $r_i$ satisfies this latter inequality, i.e., $W^\top E \Phi r_i \ge W^\top H V_0$. For this, it clearly sufficient if $\Phi r_i \ge V_0$. This however directly follows from the definition of $V_0$.
\begin{comment}

@@

\end{comment}

@@

||J^*-\hv||\leq ||J^*-\hg J^*||+||\hg J^*-\hg \hv||\leq ||J^*-\hg J^*||+\alpha || J^*- \hv||
%||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
%&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
%&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\
%&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
%&=\frac{\epsilon+\beta}{1-\alpha}.

### 2015-06-05 constsamp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments

\small

@@

\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall (s,a) \in \I,

@@

\normalsize

@@

Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n,\forall i=1,\ldots,m$. Then the constraint sampling matrix associated with the index set $\I$ is given by

@@

\M(i,j)&=1, \mb\text{if}\mb q_i=j\nn\\
&=0, \mb\text{otherwise}.

@@

\min_{r\in \N} &c^\top \Phi r\nn\\

@@

@@

where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$. Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\

@@

m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\big).

>>>>

@@

\begin{split}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb (s,a) \in \I,
\end{split}

@@

@@

Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n$, $i=1,\ldots,m$. Then the constraint sampling matrix associated with the index set $\I$ is given by

@@

\M(i,j)
=
\begin{cases}
1, & \text{ if } q_i = j;\\
0, & \text{ otherwise }.
\end{cases}

@@

\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\

@@

\end{split}

@@

where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$. The purpose of $\N$ is to ensure that the solution to the RLP is always bounded\todoc{explained the role of $\N$ and used the same in the definitions of LUB and ALUB operators}. Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\

@@

m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\left(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\right).

### 2015-06-05 grlp.tex
address some comments

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\begin{split}
\min_{r\in \chi}\, &c^\top \Phi r,\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{split}
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. \todoc{Is not $\hj\in \R^n$?
Moreover, later often $\chi$ is not taken into account. 
Also, the role of $\chi$ is never explained. Do we want to keep $\chi$ or maybe we should just remove it?
Further, $\hj$ is not really well defined. We need to defined $r_c$ and then set $\hj = \Phi r_c$.
}
Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\input{cartoon}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &c^\top \Phi r,\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{split}
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\N \subset \R^k$ is any bounded set such that $\tilde{r}_c \in \N$. \todoc{Is not $\hj\in \R^n$?
Moreover, later often $\chi$ is not taken into account. 
Also, the role of $\chi$ is never explained. Do we want to keep $\chi$ or maybe we should just remove it?
Further, $\hj$ is not really well defined. We need to defined $r_c$ and then set $\hj = \Phi r_c$.
}
\todoc{Changed the definition and using $\N$ that was used in the definition of RLP.}
Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote any solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
\begin{comment}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\end{comment}
\input{cartoon}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}

### 2015-06-05 lp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments

\begin{align}\label{mdplpshort}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J\geq T J,\\
\textbf{or}\nn\\

@@

\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &EJ\geq H J,\\

@@

\min_{r\in \R^k} &c^\top \Phi r\nn\\

@@

Unless specified otherwise we use $\tr$ to denote the solution to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. We now state the assumptions and definitions used for the rest of the paper.

@@

\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}.

@@

The modified $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}

@@

@@

The modified $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted? Also, the convention in math is to divide in the case of the $L_{\infty}$ norm. Not a high priority to change this, but maybe it would be good to do this in the longer term.}
||J||_{\infty,\rho}=\max_{s \in S} \rho(s) |J(s)|,
where $\rho \colon \S \ra \R^+$, $J\in \R^n$.

@@

>>>>

\begin{split}
\label{mdplpshort}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t}\mb &J\geq T J,
\end{split}
or 
%\text{ or }\nn\\
\begin{split}

@@

\min_{J\in \R^n} \,&c^\top J\\
\text{s.t}\mb &EJ\geq H J,
\end{split}

@@

\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\

@@

Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. We now state the assumptions and definitions used for the rest of the paper.

@@

\begin{align*}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
\end{align*}

@@

The weighted $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
\begin{align*}

@@

\end{align*}

@@

The weighted $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted? Also, the convention in math is to divide in the case of the $L_{\infty}$ norm. Not a high priority to change this, but maybe it would be good to do this in the longer term.}
\begin{align*}
||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)},
\end{align*}
where $\rho \colon \S \ra \R^+$ is the weighing function and $J\in \R^n$.

@@

\begin{align*}
